ME780 Assignment 1

### 2016-02-12 homework/homework_1/report.tex
Update report
Add traverse with noise images

@@

The inputs that drove the robot to traverse in the directions shown in 
Fig~\ref{fig:omni_robot_traverse} for 15 seconds  are as follows:

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{images/traverse_circle.jpg}
	\caption{Omni-Robot Traversing a Circle}
	\label{fig:omni_robot_circle}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{images/traverse_spiral.jpg}
	\caption{Omni-Robot Traversing a Spiral}
	\label{fig:omni_robot_spiral}
\end{figure}

@@

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.5 & 0 & 0 \\
		0 & 0.5 & 0 \\
		0 & 0 & 0.1745		
	\end{bmatrix}
\end{equation}

@@

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.1 & 0 & 0 \\
		0 & 0.1 & 0 \\
		0 & 0 & 0.1745		
	\end{bmatrix}
\end{equation}

>>>>

\begin{figure}[H]
	\centering
	\includegraphics[width=0.65\textwidth]{images/traverse_predefined_with_noise.jpg}
	\caption{Same as Fig~\ref{fig:omni_robot_predefined} but with Additive 
	Gaussian Noise}
	\label{fig:omni_robot_predefined_with_noise}
\end{figure}

@@

	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_east_with_noise.jpg}
		\caption{Traverse East}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_west_with_noise.jpg}
		\caption{Traverse West}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_north_east_with_noise.jpg}
		\caption{Traverse North East}
	\end{subfigure}

	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_south_east_with_noise.jpg}
		\caption{Traverse South East}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_inplace_with_noise.jpg}
		\caption{Traverse Inplace}
	\end{subfigure}

	\caption{Same as Fig~\ref{fig:omni_robot_traverse} but with Additive 
	Gaussian Noise}
	\label{fig:omni_robot_traverse_with_noise}
\end{figure}

The inputs that drove the robot to traverse in the directions shown in 
Fig~\ref{fig:omni_robot_traverse} and 
Fig~\ref{fig:omni_robot_traverse_with_noise}  for 15 
seconds  are as follows:

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{images/traverse_circle.jpg}
		\caption{Without Noise}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{images/traverse_circle_with_noise.jpg}
		\caption{With Noise}
	\end{subfigure}
	\caption{Omni-Robot Traversing a Circle}
	\label{fig:omni_robot_circle}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_spiral.jpg}
		\caption{Without Noise}
	\end{subfigure}

	\begin{subfigure}[b]{0.45\linewidth}
		\includegraphics[width=\textwidth]{images/traverse_spiral_with_noise.jpg}
		\caption{With Noise}
	\end{subfigure}
	\caption{Omni-Robot Traversing a Spiral}
	\label{fig:omni_robot_spiral}
\end{figure}

@@

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.5^{2} & 0 & 0 \\
		0 & 0.5^{2} & 0 \\
		0 & 0 & 0.1745^{2}		
	\end{bmatrix}
\end{equation}

@@

\begin{equation}
	Q = 
	\begin{bmatrix}
		0.1^{2} & 0 & 0 \\
		0 & 0.1^{2} & 0 \\
		0 & 0 & 0.1745^{2}		
	\end{bmatrix}
\end{equation}
